Parameterized convection, grid-scale clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-19 resolution.tex
edits

Figure~\ref{fig:cape-subt} shows the dilute CAPE values computed from mean temperature and moisture of subsiding and ascending regions in the $\pm \left( 10^{\circ}-30^{\circ} \right)$ latitude bands, hereafter referred to as the subtropics. The spread in dilute CAPE between ascending and descending grid columns is much smaller than for the deep tropics (Figure~\ref{fig:cape}a), and the dilute CAPE computed from the mean temperature and moisture over the entire subtropics varies much less with resolution compared with the deep tropics ($\sim 20$ J/kg across all resolutions, compared with $\sim 80$ J/kg across resolutions in the deep tropics). Also unlike the deep tropics, the reduction in dilute CAPE with resolution is not from an increase in occurrence of subsiding grid columns, since the space-time weights of ascending/descending motion are more-or-less invariant with resolution (Figure~\ref{fig:cape-subt}b). The decline in dilute CAPE with resolution in the subtropics is a result of increased stability due to changes in environmental temperature from the larger magnitude downward motion (not shown), but this sensitivity is not sufficient to suppress the occurrence of drizzling in the subtropics.

>>>>

Figure~\ref{fig:cape-subt} shows the dilute CAPE values computed from mean temperature and moisture of subsiding and ascending regions in the $\pm \left( 10^{\circ}-30^{\circ} \right)$ latitude bands, hereafter referred to as the subtropics. The spread in dilute CAPE between ascending and descending grid columns is much smaller than for the deep tropics (Figure~\ref{fig:cape}a), and the dilute CAPE computed from the mean temperature and moisture over the entire subtropics varies much less with resolution compared with the deep tropics ($\sim 20$ J/kg across all resolutions, compared with $\sim 80$ J/kg across resolutions in the deep tropics). Also unlike the deep tropics, the reduction in dilute CAPE with resolution is not from an increase in occurrence of subsiding grid columns, since the space-time weights of ascending/descending motion are more-or-less invariant with resolution (Figure~\ref{fig:cape-subt}b). The decline in dilute CAPE with resolution in the subtropics is a result of increased stability due to changes in environmental temperature from the larger magnitude downward motion (not shown), but this sensitivity is not sufficient oppose the instability generated by the global maximum in latent heat fluxes.
